---
title: "Import the Japanese FDI data: 東洋経済データの読み込み"
author: "Ayumu Tanaka"
date: "2024-05-18"
output:
  html_document:
    toc: true
    toc_float: true
    number_sections: yes
#bibliography: ref.bib
link-citations: yes
---

```{r setup-chunk, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, # Display codes
                      cache = FALSE, # do not Cache the results
                      message=FALSE, # Suppress messages
                      warning=FALSE) # Suppress warnings

```

# Preparation


```{r preparation}
# Remove all data
rm(list = ls())

# Load the necessary libraries
library("rio")           # For importing data 
library("tidyverse")     # For data manipulation
library("countrycode")   # For creating the country ISO codes
library("Hmisc")         # For labeling the variables
```




# Load the data "SHJP", "JP", and "FA"

- "SHJP": Japanese parent firms' ownership data
- "JP": Japanese parent firms' financial data
- "FA": Japanese affiliates' basic data

以下のデータを読み込む。

- "SHJP": 日本の親会社の出資比率データ
- "JP": 日本の親会社の財務データ
- "FA": 日本の海外子会社の基本データ

```{r load-data}

  # Japanese parent firms' ownership data
  SHJP <- rio::import("../Data_raw/KSKSHJP.dta") 
    # Create the year variable by subtracting 1 from the EditionYear    
    SHJP$year =  SHJP$EditionYear-1
    # Remove "EditionYear" column
    SHJP$EditionYear = NULL
    # Remove if KSJOwnRatio < 10
    SHJP = SHJP[SHJP$KSJOwnRatio >= 10, ]
    # order by KSKJPCode and year
    SHJP = SHJP[order(SHJP$KSKJPCode, SHJP$year), ]
    
  # Japanese parent firms' financial data
  JP <- rio::import("../Data_raw/KSKJP.dta")
    # Create the year variable by subtracting 1 from the EditionYear   
    JP$year =  JP$EditionYear-1 
    # Remove "EditionYear" column
    JP$EditionYear = NULL
    JP = JP[order(JP$KSKJPCode, JP$year), ]

    
  # Japanese affiliates' basic data
  FA <- rio::import("../Data_raw/KSKFA.dta")
    # Create the year variable by subtracting 1 from the EditionYear
    FA$year =  FA$EditionYear-1
    # Remove "EditionYear" column
    FA$EditionYear = NULL
    # Order by KSFAffiliateCode and year
    FA = FA[order(FA$KSFAffiliateCode, FA$year), ]
    FA = FA[FA$KSFParentJPOwnRatio >= 10, ]
    
```


# Variable Names

## SHJP

```{r check-variable-names1}
names(SHJP)
```

## JP

```{r check-variable-names2}
names(JP)
```

## FA

```{r check-variable-names3}
names(FA)
```


# Data preparation of FA data

必要な変数を残し、変数名を変更しておく。

```{r}
# Remove unnecessary columns
FA <- FA %>% 
   select(-c(KSFDistCode1990, KSFDistCode1995,KSFAffiliateNameAlph,KSFAddressAlph,
             KSFAddress, KSFPhoneNumber, KSFDescription, KSFRepresentative,
             KSFCapitalStockNumeric, KSFCapitalStockDigitString,
             KSFCapitalStockCurrencySymbol, KSFDispatchedNumber, KSFStartDateType,
             KSFFiscalPeriodDate, KSFRevenueNumeric, 
             KSFRevenueDigitString, KSFRevenueCurrencySymbol, KSFRevenueUSD
             ))
 


# Remove "KSF" from the columns names
   names(FA) <- gsub("KSF", "", names(FA))
   
# Add "Parent_" to the column names starting "Sector"
  names(FA) <- gsub("^Sector", "FA_Sector", names(FA))
```


# Data preparation of SHJP data

必要な変数を残し、変数名を変更しておく。


```{r}
# Remove "KSF" from the columns names
      names(SHJP) <- gsub("KSK", "", names(SHJP))
      names(SHJP) <- gsub("KSF", "", names(SHJP))
      names(SHJP) <- gsub("KS", "", names(SHJP))
```


```{r filter-largest-owner-SHJP}
# Sort the rows by AffiliateCode, year, and JOwnRatio
SHJP <- SHJP %>%
  arrange(AffiliateCode, year, desc(JOwnRatio))

# Create the variable that show the ranking of JOwnRatio at AffiliateCode-year
SHJP <- SHJP %>%
  group_by(AffiliateCode, year) %>%
  mutate(rank = rank(-JOwnRatio, ties.method = "min", na.last = "keep")) %>%
  ungroup()
```


# Data preparation of JP data

必要な変数を残し、変数名を変更しておく。

```{r}

# Remove "KSK" from the column names of JP
  names(JP) <- gsub("KSK", "", names(JP))
  
# Add "Parent_" to the column names starting "Common"
  names(JP) <- gsub("^Common", "Parent_", names(JP))

# Add "Parent_" to the column names starting "Sector"
  names(JP) <- gsub("^Sector", "Parent_Sector", names(JP))

  
  # Select the necessary columns from JP
JP <- JP %>% 
  select(JPCode, year, Parent_Name, Parent_NameAlphabet, 
         Parent_SectorCode1990, Parent_SectorCode2000, Parent_SectorCode2009
         )

```



# Export the data

```{r export-data}
# Export the data
  rio::export(SHJP, "../Data_output/SHJP.rds")
  rio::export(FA, "../Data_output/FA.rds")
  rio::export(JP, "../Data_output/JP.rds")

```



