---
title: "Brexit firms"
author: "Ayumu Tanaka"
date: "2024-05-30"
output:
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    #keep_md: true
---

```{r setup-chunk, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, # show R code
                      cache = FALSE, # cache results
                      message=FALSE, # show messages
                      warning=FALSE) # show warnings

```


# Parent-level
## Load the data
```{r}
library(rio)
parent_last = import("../Data_output/parent_last.rds")

# The firms that have affiliates in the United Kingdom (GBR).
GBR <- subset(parent_last, parent_last$iso=="GBR")

```


## Density function of ownership ratio
```{r density-ratio}
library(ggplot2)

# Draw the density function of "Ratio" by "censored==1 and 0. Set transparency is 0.5.
Figure_ratio <- ggplot(GBR, aes(x=Ratio)) + 
  geom_density(data=subset(GBR, censored==0), 
               aes(x=Ratio), fill="red", alpha=0.4) + 
  geom_density(data=subset(GBR, censored==1), 
               aes(x=Ratio), fill="blue", alpha=0.4) +
    labs(caption = "Blue = firms surviving in the UK, Red = firms exiting from the UK",
         x = "Japanese parent firms' ownership ratio") +
  theme_minimal()

Figure_ratio
```

## Density function of No. of affiliates 
```{r density-aff}
# Draw the density function of "N" by "censored==1 and 0. Set transparency is 0.4.
Figure_N_Aff <- ggplot(GBR, aes(x=N_Aff)) + 
  geom_density(data=subset(GBR, censored==0), 
               aes(x=N_Aff), fill="red", alpha=0.4) + 
  geom_density(data=subset(GBR, censored==1), 
               aes(x=N_Aff), fill="blue", alpha=0.4) +
    labs(caption = "Blue = firms surviving in the UK, Red = firms exiting from the UK",
         x = "Number of affiliates") +
  theme_minimal()

Figure_N_Aff
```

## Collapse the data by iso and year

```{r collapse-data}
library(dplyr)

# Make the year2 which is equal to year + 1 
parent_last$year2 <- parent_last$year + 1

# Replace the year2 with year if year <=2016
parent_last$year2 <- ifelse(parent_last$year<=2016, 
                            parent_last$year, parent_last$year2)

# Replace the year2 with year if year == 2018 | year == 2020 
parent_last$year2 <- ifelse(parent_last$year==2018 |
                            parent_last$year==2020,
                            parent_last$year,parent_last$year2)

# Collapse the data by iso and year2
collapse <- parent_last %>% 
  group_by(iso, year2) %>% 
  summarise(N = n(), 
            WN = sum(Ratio))

# Drop if year==2022
collapse <- subset(collapse, year2!=2022)

# Rename year2 as year, rename N as N_exit
N_firm_exit <- collapse %>% 
  rename(year = year2, N_exit = N)


rio::export(N_firm_exit, "../Data_output/N_firm_exit.rds")

```


## Brexit firm

```{r Brexit-firm-dummy}
# Make the sample of Brexit==1
Firm_UK <- subset(parent_last, iso=="GBR")
# Make the sample of exit==1
exit_firm <- subset(parent_last, censored==0)

exit_firm_UK <- subset(exit_firm, iso=="GBR")
# Make the sample of exit==1 & year >= 2016
exit_firm2016 <- subset(parent_last, censored==0 & year>=2016)
exit_firm2016_UK <- subset(exit_firm, iso=="GBR" & year>=2016)

rio::export(exit_firm2016_UK, "../Data_output/exit_firm2016_UK.rds")

```



## Plot the sector of the firms exiting from the UK
```{r fig_plot_sector, dpi = 200}

# Collapse the data "exit_firm_UK" by Parent_SectorClassNameAlph
exit_firm_UK_sector <- exit_firm2016_UK %>% 
  group_by(Parent_SectorClassNameAlph) %>% 
  summarise(N = n())

# Sort the data by N
exit_firm_UK_sector <- exit_firm_UK_sector %>% 
  arrange(desc(N))

# Create the rank of the sector based on N
exit_firm_UK_sector$rank <- 1:nrow(exit_firm_UK_sector)

# Total number of firms
n_firm = nrow(exit_firm2016_UK)
n_firm_cap = paste0("Total number = ", n_firm)

# Plot the horizontal bar of N by Parent_SectorClassNameAlph
## The order of the bar is based on rank
## Add the value label on the top of the bar
f1 <- ggplot(exit_firm_UK_sector, 
       aes(x = reorder(Parent_SectorClassNameAlph, -rank), y = N)) +
  geom_bar(stat = "identity", alpha = 0.4) +
  geom_text(aes(label = N), hjust = 1.0, size = 2) +
  labs(title = "Parent-level",
      caption = n_firm_cap,
       x = "Sector",
       y = "Number of firms") +
  theme_minimal() +
  coord_flip()   # This flips the x and y axes to make it horizontal 

f1
```



## Plot the number of firms exiting from the UK & other High-income EU countries

High-income EU countries are Luxembourg, Ireland, Denmark, Netherlands, Sweden, Austria, Germany, Finland, Belgium, France, United Kingdom, and Italy. The GDP per capita of these countries are as follows:

- Luxembourg: $115,531 LUX *
- Ireland: $84,339 IRL *
- Denmark: $63,434 DNK *
- Netherlands: $62,515 NLD *
- Sweden: $59,738 SWE *
- Austria: $57,256 AUT *
- Germany: $55,682 DEU *
- Finland: $55,345 FIN *
- Belgium: $54,319 BEL*
- France: $46,133 FRA *
- United Kingdom: $45,470 GBR *
- Italy: $40,594 ITA *

```{r fig_plot_exit-compare, dpi = 300}
# Identify high-income EU countries
EU_HI <- c("AUT", "BEL", "DNK", "FIN", "FRA", "DEU", "IRL", "ITA", "LUX", "NLD", "SWE", "GBR")
# Create the EU dummy
collapse$EU_HI <- ifelse(collapse$iso %in% EU_HI, 1, 0)
# Keep the data of EU_HI
collapse_EU_HI <- subset(collapse, EU_HI==1)
# Create the GBR dummy
collapse_EU_HI$GBR <- ifelse(collapse_EU_HI$iso=="GBR", 1, 0)
# Collapse the data by year2 and GBR
library(doBy)
collapseNse <- doBy::summaryBy(N ~ year2 + GBR, FUN=c(mean,sd), data = collapse_EU_HI)
# Replace N.sd = 0 if GBR==1
collapseNse$N.sd[collapseNse$GBR==1] <- 0
# Create the Group dummy
collapseNse$Group <- ifelse(collapseNse$GBR==1, "GBR", "High-income EU countries")

# Keep year2>=2010
collapseNse <- subset(collapseNse, year2>=2010)

# Plot the mean number of observation exiting by Group with 95% CI

library(ggplot2)
ggplot(data = subset(collapseNse, GBR==0), 
                      aes(x = year2, y = N.mean, 
                          color = Group)) +
  geom_line(linetype = "dotted") +
  geom_point() +
  geom_ribbon(aes(ymin = N.mean - 1.96 * N.sd, 
                  ymax = N.mean + 1.96 * N.sd, 
                  fill = Group), alpha = 0.2,
              linetype = "dotted") +
  labs(title = "Number of exiting Japanese parent firms",
       x = "Year",
       y = "Number of exiting firms") +
  theme_minimal() +
  geom_line(data = subset(collapseNse, GBR==1), 
            linetype = "solid",
            colour = "black") +
  geom_point(data = subset(collapseNse, GBR==1),
             colour = "black") +
  geom_text(data = subset(collapseNse, GBR==1),
             aes(label = N.mean),
                        nudge_y = 2,
            #position = position_stack(vjust = 1.07),
            colour =  "black") +
  theme(legend.position = "none") +
  geom_vline(xintercept = 2016, linetype = "dotted") + # vertical line at 2016
  labs(caption = "Solid line: UK. Dotted line: High-income EU countries.") +
  theme(plot.caption = element_text(hjust = 0, size = 8)) +
  annotate("text", x = 2016, y = 45, 
           label = "Brexit referendum",
           , colour = "blue") +
  annotate("text", x = 2013, y = 40, 
           label = "UK", colour = "black") + 
  annotate("text", x = 2013, y = 0, 
           label = "High-income EU countries",
           colour = "red") +
  scale_x_continuous(breaks = ~ axisTicks(., log = FALSE)) 
```


## Plot the number of firms exiting from the UK

```{r fig_plot_exit, dpi = 300}
library(ggplot2)

# Create the subset of collapse if iso == "GBR"
collapseGBR <- subset(collapse, iso=="GBR")

# Plot the number of observation exiting from the UK
Figure_exit <- ggplot(collapseGBR, aes(x = year2, y = N)) +
  geom_bar(stat = "identity", alpha = 0.4) +
  labs(title = "Number of Japanese parent firms exiting from the UK",
       x = "Year",
       y = "Number of firms") +
  theme_minimal() 

# Add the label of bar height over the bar
Figure_exit <- Figure_exit + geom_text(aes(label = N), vjust = -0.3)
  
# Add the vertical line at year == 2016
Figure_exit <- Figure_exit + geom_vline(xintercept = 2016, linetype = "dotted")

# Add the text "Brexit referendum" at year == 2016
Figure_exit <- Figure_exit + annotate("text", x = 2016, y = 70, label = "Brexit referendum")

# Display the bar plot
Figure_exit
```

# Affiliate-level
## Load the data
```{r}
library(rio)
aff_last = rio::import("../Data_output/aff_last.rds")
```

## Brexit affiliate

```{r Brexit-aff-dummy}
# Make the sample of Brexit==1
aff_UK <- subset(aff_last, iso=="GBR")
# Make the sample of exit==1
exit_aff <- subset(aff_last, censored==0)
exit_aff_UK <- subset(exit_aff, iso=="GBR")
# Make the sample of exit==1 & year >= 2016
exit_aff2016 <- subset(aff_last, censored==0 & year>=2016)
exit_aff2016_UK <- subset(exit_aff, iso=="GBR" & year>=2016)

rio::export(exit_aff2016_UK, "../Data_output/exit_aff2016_UK.rds")

```

## Plot the sector of the firms exiting from the UK
```{r fig_plot_sector-aff, dpi = 200}
library(tidyverse)
# Collapse the data "exit_firm_UK" by Parent_SectorClassNameAlph
exit_aff_UK_sector <- exit_aff2016_UK %>% 
  group_by(FA_SectorClassNameAlph) %>% 
  summarise(N = n())

# Sort the data by N
exit_aff_UK_sector <- exit_aff_UK_sector %>% 
  arrange(desc(N))

# Create the rank of the sector based on N
exit_aff_UK_sector$rank <- 1:nrow(exit_aff_UK_sector)

# Total number of affiliates
n_aff = nrow(exit_aff2016_UK)
n_aff_cap = paste0("Total number = ", n_aff)

# Plot the horizontal bar of N by Parent_SectorClassNameAlph
## The order of the bar is based on rank
## Add the value label on the top of the bar
a1 <- ggplot(exit_aff_UK_sector, 
       aes(x = reorder(FA_SectorClassNameAlph, -rank), y = N)) +
  geom_bar(stat = "identity", alpha = 0.4) +
  geom_text(aes(label = N), hjust = 1.5,  size = 2) +
  labs(title = "Affiliate-level",
       caption = n_aff_cap,
       x = "Sector",
       y = "Number of affiliates") +
  theme_minimal() +
  coord_flip()   # This flips the x and y axes to make it horizontal 


a1
```

## Collapse the data by iso and year

```{r collapse-data-aff}
library(dplyr)

# Make the year2 which is equal to year + 1 
aff_last$year2 <- aff_last$year + 1

# Replace the year2 with year if year <=2016
aff_last$year2 <- ifelse(aff_last$year<=2016, 
                            aff_last$year, aff_last$year2)

# Replace the year2 with year if year == 2018 | year == 2020 
aff_last$year2 <- ifelse(aff_last$year==2018 |
                            aff_last$year==2020,
                            aff_last$year,aff_last$year2)

# Collapse the data by iso and year2
collapse_aff <- aff_last %>% 
  group_by(iso, year2) %>% 
  summarise(N = n(), 
            WN = sum(Ratio/100))

# Drop if year==2022
collapse_aff <- subset(collapse_aff, year2!=2022)

# Rename year2 as year, rename N as N_exit
N_Aff_exit <- collapse_aff %>% 
  rename(year = year2, N_exit = N)

rio::export(N_Aff_exit, "../Data_output/N_Aff_exit.rds")
```

## Plot the number of firms exiting from the UK & other High-income EU countries

High-income EU countries are Luxembourg, Ireland, Denmark, Netherlands, Sweden, Austria, Germany, Finland, Belgium, France, United Kingdom, and Italy. The GDP per capita of these countries are as follows:

- Luxembourg: $115,531 LUX *
- Ireland: $84,339 IRL *
- Denmark: $63,434 DNK *
- Netherlands: $62,515 NLD *
- Sweden: $59,738 SWE *
- Austria: $57,256 AUT *
- Germany: $55,682 DEU *
- Finland: $55,345 FIN *
- Belgium: $54,319 BEL*
- France: $46,133 FRA *
- United Kingdom: $45,470 GBR *
- Italy: $40,594 ITA *

```{r Fig2a_plot_exit-compare-aff, dpi = 300}
# Identify high-income EU countries
EU_HI <- c("AUT", "BEL", "DNK", "FIN", "FRA", "DEU", "IRL", "ITA", "LUX", "NLD", "SWE", "GBR")
# Create the EU dummy
collapse_aff$EU_HI <- ifelse(collapse_aff$iso %in% EU_HI, 1, 0)
# Keep the data of EU_HI
collapse_aff_EU_HI <- subset(collapse_aff, EU_HI==1)
# Create the GBR dummy
collapse_aff_EU_HI$GBR <- ifelse(collapse_aff_EU_HI$iso=="GBR", 1, 0)
# Collapse the data by year2 and GBR
library(doBy)
collapse_affNse <- doBy::summaryBy(N ~ year2 + GBR, FUN=c(mean,sd), data = collapse_aff_EU_HI)
# Replace N.sd = 0 if GBR==1
collapse_affNse$N.sd[collapse_affNse$GBR==1] <- 0
# Create the Group dummy
collapse_affNse$Group <- ifelse(collapse_affNse$GBR==1, "GBR", "High-income EU countries")

# Keep year2>=2010
collapse_affNse <- subset(collapse_affNse, year2>=2010)

# Plot the mean number of observation exiting by Group with 95% CI

library(ggplot2)
ggplot(data = subset(collapse_affNse, GBR==0), 
                      aes(x = year2, y = N.mean, 
                          color = Group)) +
  geom_line(linetype = "dotted") +
  geom_point() +
  geom_ribbon(aes(ymin = N.mean - 1.96 * N.sd, 
                  ymax = N.mean + 1.96 * N.sd, 
                  fill = Group), alpha = 0.2,
              linetype = "dotted") +
  labs(title = "Number of exiting Japanese affiliates",
       x = "Year",
       y = "Number of exiting affiliates") +
  theme_minimal() +
  geom_line(data = subset(collapse_affNse, GBR==1), 
            linetype = "solid",
            colour = "black") +
  geom_point(data = subset(collapse_affNse, GBR==1),
             colour = "black") +
  geom_text(data = subset(collapse_affNse, GBR==1),
             aes(label = N.mean),
                        nudge_y = 7,
            #position = position_stack(vjust = 1.07),
            colour =  "black") +
  theme(legend.position = "none") +
  geom_vline(xintercept = 2016, linetype = "dotted") + # vertical line at 2016
  labs(caption = "Solid line: UK. Dotted line: High-income EU countries.") +
  theme(plot.caption = element_text(hjust = 0, size = 8)) +
  annotate("text", x = 2016, y = 85, 
           label = "Brexit referendum",
           , colour = "blue") +
  annotate("text", x = 2013, y = 80, 
           label = "UK", colour = "black") + 
  annotate("text", x = 2013, y = 0, 
           label = "High-income EU countries",
           colour = "red") +
  scale_x_continuous(breaks = ~ axisTicks(., log = FALSE)) 


# Save the figure as EPS
ggsave("../EPS/Fig2a_plot_exit-compare-aff.eps", dpi = 300)


```


## Combine two figures
```{r fig-n-exit, dpi = 300}
library(gridExtra)
# Combine two figures: a1 and f1
grid.arrange(a1, f1, nrow = 1)

```


```{r}
library(gridExtra)
library(ggplot2)

# Combine two figures: a1 and f1
c1 <- arrangeGrob(a1, f1, nrow = 1)  # arrangeGrob

# 保存
ggsave("../EPS/FigX3-sector.png", c1, width = 10, height = 5, dpi = 300)

```


# Survival years of the firms exiting from the UK

```{r fig-histgram-survival, dpi = 300}
## Histgram of survival years: affiliate
subtitle <- paste0("N =", nrow(exit_aff2016_UK))
sya <- ggplot(exit_aff2016_UK, aes(x = survival_years)) +
  geom_histogram(binwidth = 1, fill = "blue", alpha = 0.4) +
  labs(title = "Japanese affiliates exiting from the UK",
       x = "Survival years",
       y = "Number of affiliates",
       subtitle = subtitle) +
  theme_minimal()

## Histgram of survival years: parent firm
subtitle <- paste0("N =", nrow(exit_firm2016_UK))
syp <- ggplot(exit_firm2016_UK, aes(x = survival_years)) +
  geom_histogram(binwidth = 1, fill = "red", alpha = 0.4) +
  labs(title = "Japanese parent firms exiting from the UK",
       x = "Survival years",
       y = "Number of firms",
       subtitle = subtitle) +
  theme_minimal()

## Combine two figures
grid.arrange(sya, syp, nrow = 2)


```


# Aff_size of the firms exiting from the UK

```{r fig-aff-size, dpi = 300}

## Drop NA obs
exit_aff2016_UK2 <- subset(exit_aff2016_UK, !is.na(exit_aff2016_UK$Aff_size))

# Subtitle
subtitle <- paste0("N=", nrow(exit_aff2016_UK2), 
                   " Mean=", round(mean(exit_aff2016_UK2$Aff_size), 1))

## Replace 0 with 1
exit_aff2016_UK2$Aff_size <- ifelse(exit_aff2016_UK2$Aff_size==0, 1, exit_aff2016_UK2$Aff_size)

## Create a category variable: Aff_size: 0-10, 11-50, 50-100, 100+
exit_aff2016_UK2$Aff_size_cat <- cut(exit_aff2016_UK2$Aff_size, 
                               breaks = c(0, 10, 50, 100, 100000), 
                               labels = c("0-10", "11-50", "51-100", "100+"))

## Order Aff_size & Aff_size_cat 
exit_aff2016_UK2 <- exit_aff2016_UK2 %>% 
  select(Aff_size, Aff_size_cat, everything())

## Barplot of Aff_size_cat: affiliate
sizea2 <- ggplot(exit_aff2016_UK2, aes(x = Aff_size_cat)) +
  geom_bar(fill = "blue", alpha = 0.4) +
  labs(title = "Japanese affiliates exiting from the UK",
       x = "Affiliate size (Number of employees)",
       y = "Number of affiliates",
       subtitle = subtitle) +
  theme_minimal()

sizea2

ggsave("../EPS/FigX1-aff-size-aff.png", dpi = 300)


```

