---
title: "Number of Affiliates"
author: "Ayumu Tanaka"
date: "2025-06-06"
output:
  html_document:
    toc: true
    toc_float: true
    number_sections: yes
    keep_md: true
#bibliography: ref.bib
#link-citations: yes
---

```{r setup-chunk, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, # show R code
                      cache = FALSE, # do not cache results
                      message=FALSE, # do not show messages
                      warning=FALSE) # do not show warnings

```

# Load the package

```{r load-package}
library(ggplot2)
library(dplyr)
```

# Load the data

```{r load-data-package}
library(rio)
FA6 = import("../Data_output/FA6.rds")

# Keep years: 2010 to 2020
FA6 <- subset(FA6, year >= 2010 & year <= 2020)

names(FA6)[names(FA6)=="iso"] = "country"


```




# Collapse the data by country and year with `tidyverse`

```{r collapse-data-tidyverse}
N_Aff <- FA6 %>% 
  group_by(year, country) %>% 
  summarise(N = n(), 
            EU = first(EU_all),
            meanratio = mean(RatioAll, na.rm = TRUE),
            WN = sum(RatioAll, na.rm = TRUE)
            )
```



# Subsample of DEU and GBR

```{r subsample}
# Subsample of DEU and GBR
  N_Aff_DEU <- filter(N_Aff, country %in% c("DEU", "GBR")) 
# Subsample of year>=2010
  N_Aff_DEU <- filter(N_Aff_DEU, year >= 2010)
```



# Make the collapsed data by GBR

```{r collapse-data-GBR}
# Make subsample of aff if EU_all == 1
  aff_EU <- subset(FA6, FA6$EU_all == 1)
# Subsample of year>=2010
  aff_EU <- subset(aff_EU, aff_EU$year >= 2010)

# Collapse the data by GBR and year
N_Aff_EU <- aff_EU %>% 
  group_by(year, GBR) %>% 
  summarise(N = n(), 
            GBR = first(GBR),
            ncountry = n_distinct(country),
            WN = sum(RatioAll, na.rm = TRUE))

```

# High-income EU countries

- High-income EU countries are Luxembourg, Ireland, Denmark, Netherlands, Sweden, Austria, Germany, Finland, Belgium, France, United Kingdom, and Italy. The GDP per capita of these countries are as follows:
- Luxembourg: $115,531 LUX
- Ireland: $84,339 IRL
- Denmark: $63,434 DNK
- Netherlands: $62,515 NLD
- Sweden: $59,738 SWE
- Austria: $57,256 AUT
- Germany: $55,682 DEU
- Finland: $55,345 FIN
- Belgium: $54,319 BEL 
- France: $46,133 FRA
- United Kingdom: $45,470 GBR
- Italy: $40,594 ITA

```{r high-income-EU}


# Create high-income EU member variable
aff_EU$highEU <- ifelse(aff_EU$country %in% c("AUT", "BEL", "DNK", "FIN", "FRA", "DEU", "IRL", "ITA", "LUX", "NLD", "SWE", "GBR"), 1, 0)

# Create the subsample of high-income EU countries
aff_EU_high <- subset(aff_EU, aff_EU$highEU == 1)


# Collapse the data by GBR and year
N_Aff_EU_high <- aff_EU_high %>% 
  group_by(year, GBR) %>% 
  summarise(N = n(), 
            GBR = first(GBR),
            ncountry = n_distinct(country),
            WN = sum(RatioAll, na.rm = TRUE)
            )

```





# Export the data
- To avoid the conflict with `plotly`'s `export`, use `rio::export` instead of `export`.

```{r save-data}
library("rio")
  rio::export(N_Aff, "../Data_output/N_Aff.rds")
  rio::export(N_Aff_EU, "../Data_output/N_Aff_EU.rds")
  rio::export(N_Aff_EU_high, "../Data_output/N_Aff_EU_high.rds")
  rio::export(N_Aff_DEU, "../Data_output/N_Aff_DEU.rds")
  rio::export(aff_EU, "../Data_output/aff_EU.rds")
  rio::export(aff_EU_high, "../Data_output/aff_EU_high.rds")
  
  rio::export(N_Aff, "../Data_output/N_Aff.dta")
```







# Appendix: Collapse the data by country and year with `doBy` {-}


```
# collapse the data by country and year
library(doBy)
N_Aff1 = summaryBy(AffiliateCode + Ratio ~ year + country, 
                  FUN = c(length, sum), data = aff)

# Rename the columns
names(N_Aff1)[names(N_Aff1)=="AffiliateCode.length"] = "N"
names(N_Aff1)[names(N_Aff1)=="Ratio.sum"] = "WN"

# Remove unnecessary columns "Ratio.length" and "AffiliateCode.sum"
N_Aff1$AffiliateCode.sum <- NULL
N_Aff1$Ratio.length <- NULL

```
