---
title: "New entry: Another approach"
author: "Ayumu Tanaka"
date: "2024-05-29"
output:
  html_document:
    toc: true
    toc_float: true
    number_sections: yes
    #keep_md: true
#bibliography: ref.bib
#link-citations: yes
---

```{r setup-chunk, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, # show R code
                      cache = FALSE, # cache results
                      message=FALSE, # do not show messages
                      warning=FALSE) # do not show warnings

```


# Introduction

Define the first year as the year when a new affiliate appears in the data for the first time.


# Load the package

```{r load-package}
library(ggplot2)
library(dplyr)
```

# Load the data

```{r load-data-package}
library(rio)
aff = rio::import("../Data_output/FA6.rds")

```


- check the years in the data

```{r check-years}
table(aff$year)
```


- Keep bi-annual data from 1990 to 2020
- 2017や2019 が含まれていると、2016--2020年の期間の新規参入数が小さくなってしまうので、全期間２年ごとにデータを抽出する。

```{r keep-bi-annual-data}
# Keep bi-annual data from 1990 to 2020: 1990, 1992, 1994, 1996, 1998, 2000, 2002, 2004, 2006, 2008, 2010, 2012, 2014, 2016, 2018, 2020
aff = aff %>% filter(year %in% seq(1990, 2020, by = 2))
# check the years in the data
table(aff$year)
```





# Affiliate-level data
## Keep the first year of the data

```{r keep-first-year}
aff_first <- aff %>% 
  group_by(AffiliateCode) %>% 
  filter(year == min(year)) %>% 
  ungroup()
```

## Collapse the data by industry, iso and start year

```{r collapse-data-tidyverse-sector}
collapseIndustry <- aff_first %>% 
  group_by(year, iso, FA_SectorCode2009) %>% 
  summarise(N = n(), 
            EU = first(EU_all),
            meanratio = mean(Ratio, na.rm = TRUE),
            WN = sum(Ratio))

# Export the data
rio::export(collapseIndustry, "../Data_output/collapse_industry.rds")
rio::export(collapseIndustry, "../Data_output/collapse_industry.dta")

```


## Collapse the data by iso and start year

```{r collapse-data-tidyverse}
collapse <- aff_first %>% 
  group_by(year, iso) %>% 
  summarise(N = n(), 
            EU = first(EU_all),
            meanratio = mean(Ratio, na.rm = TRUE),
            WN = sum(Ratio))

# Export the data
rio::export(collapse, "../Data_output/collapse.rds")
rio::export(collapse, "../Data_output/collapse.dta")
```




## Data cleaning

High-income EU countries are Luxembourg, Ireland, Denmark, Netherlands, Sweden, Austria, Germany, Finland, Belgium, France, United Kingdom, and Italy. The GDP per capita of these countries are as follows:

- Luxembourg: $115,531 LUX *
- Ireland: $84,339 IRL *
- Denmark: $63,434 DNK *
- Netherlands: $62,515 NLD *
- Sweden: $59,738 SWE *
- Austria: $57,256 AUT *
- Germany: $55,682 DEU *
- Finland: $55,345 FIN *
- Belgium: $54,319 BEL*
- France: $46,133 FRA *
- United Kingdom: $45,470 GBR *
- Italy: $40,594 ITA *

```{r collapsed-data2}

# Keep year>=2010  & year <=2020
collapse <- subset(collapse, year >= 2010 & year <=2020)


# Identify high-income EU countries
EU_HI <- c("AUT", "BEL", "DNK", "FIN", "FRA", "DEU", "IRL", "ITA", "LUX", "NLD", "SWE", "GBR")
# Create the EU dummy
collapse$EU_HI <- ifelse(collapse$iso %in% EU_HI, 1, 0)
# Keep the data of EU_HI
collapse_EU_HI <- subset(collapse, EU_HI==1)
# Create the GBR dummy
collapse_EU_HI$GBR <- ifelse(collapse_EU_HI$iso=="GBR", 1, 0)
# Collapse the data by year2 and GBR
library(doBy)
collapseNse <- doBy::summaryBy(N ~ year + GBR, FUN=c(mean,sd), 
                               data = collapse_EU_HI)
# Replace N.sd = 0 if GBR==1
collapseNse$N.sd[collapseNse$GBR==1] <- 0
# Create the Group dummy
collapseNse$Group <- ifelse(collapseNse$GBR==1, "GBR", "High-income EU countries")

```



## Plot the number of firms entering the UK & other High-income EU countries

```{r Fig2b_plot_enter-aff-compare, dpi = 300}
# Plot the mean number of observation exiting by Group with 95% CI

library(ggplot2)
ggplot(data = subset(collapseNse, GBR==0), 
                      aes(x = year, y = N.mean, 
                          color = Group)) +
  geom_line(linetype = "dotted") +
  geom_point() +
  geom_ribbon(aes(ymin = N.mean - 1.96 * N.sd, 
                  ymax = N.mean + 1.96 * N.sd, 
                  fill = Group), alpha = 0.2,
              linetype = "dotted") +
  labs(title = "Number of new affiliates",
       x = "Year",
       y = "Number of new affiliates") +
  theme_minimal() +
  geom_line(data = subset(collapseNse, GBR==1), 
            linetype = "solid",
            colour = "black") +
  geom_point(data = subset(collapseNse, GBR==1),
             colour = "black") +
  geom_text(data = subset(collapseNse, GBR==1),
             aes(label = N.mean),
            nudge_y = 3.5,
            #position = position_stack(vjust = 1.4),
            colour =  "black") +
  theme(legend.position = "none") +
  geom_vline(xintercept = 2016, linetype = "dotted") + # vertical line at 2016
  labs(caption = "Solid line: UK. Dotted line: High-income EU countries.") +
  theme(plot.caption = element_text(hjust = 0, size = 8)) +
  annotate("text", x = 2017, y = 75, 
           label = "Brexit referendum",
           , colour = "blue") +
  annotate("text", x = 2011, y = 70, 
           label = "UK", colour = "black") + 
  annotate("text", x = 2014, y = 0, 
           label = "High-income EU countries",
           colour = "red") +
  scale_x_continuous(breaks = ~ axisTicks(., log = FALSE)) 

# Save the plot as EPS
ggsave("../EPS/Fig2b_plot_enter-aff-compare.eps", dpi = 300)

```




