---
title: "Affiliate data & Country-level data: 子会社データと国データの接続"
author: "Ayumu Tanaka"
date: "2024-05-18"
output:
  html_document:
    toc: true
    toc_float: true
    number_sections: yes
#bibliography: ref.bib
link-citations: yes
---

```{r setup-chunk, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, # Display codes
                      cache = FALSE, # do not Cache the results
                      message=FALSE, # Suppress messages
                      warning=FALSE) # Suppress warnings

```

# Preparation


```{r preparation}
# Remove all data
rm(list = ls())

# Load the necessary libraries
library("rio")           # For importing data 
library("tidyverse")     # For data manipulation
library("countrycode")   # For creating the country ISO codes
library("Hmisc")         # For labeling the variables
```




# Load the data データ読み込み


以下のデータを読み込む。

- "FA3": 日本の海外子会社の基本データ

```{r load-data}

FA3  <- rio::import("../Data_output/FA3.rds")
JP2   <- rio::import("../Data_output/JP2.rds")
SHJP <- rio::import("../Data_output/SHJP.rds")

```


# Largest Owner

```{r ranking-largest-owner}
# Check the rank
barplot(table(SHJP$rank), 
        main = "Number of Affiliates by Rank of Parent Firm",
        xlab = "Rank of Parent Firm",
        ylab = "Number of Affiliates",
        col = "lightblue"
        )
```


第1位の親会社に絞る。

```{r filter-largest-owner-SHJP}

# Keep only the largest values of JOwnRatio at JPCode-year
  SHJP2 <- SHJP %>%
    filter(rank == 1) 

```

# Check the duplicates 

```{r}
# Check the duplicates in JPCode and year
  duplicates <- SHJP2 %>%
    group_by(AffiliateCode, year) %>%
    filter(n() > 1) %>%
    ungroup
```



```{r check-duplicates}
# Create the count variable within AffiliateCode-year
  SHJP2 <- SHJP2 %>%
    group_by(AffiliateCode, year) %>%
    mutate(count = n()) %>%
    ungroup()
```

```{r}
barplot(table(SHJP2$count), 
        main = "Number of Affiliates by Count of Parent Firm",
        xlab = "Count of Parent Firm",
        ylab = "Number of Affiliates",
        col = "lightblue"
        )
```



# Remove the duplicates
```{r}
SHJP3 <- SHJP2 %>%
  filter(count == 1) %>%
  select(-count) # Remove the count variable

# Remove duplicates in terms of AffilateCode and year
SHJP3 <- SHJP3 %>%
  group_by(AffiliateCode, year) %>%
  filter(n() == 1) %>%
  ungroup()
```


# Ownership data & Parent firms' financial data

Combine the Japanese ownership data "SHJP" with the Japanese parent firms' financial data "JP"

```{r combine-JP-data}

SHJP4 <- left_join(SHJP3, JP2,
                           by = c("JPCode" = "JPCode", 
                                  "year" = "year"))


# Remove duplicates in terms of AffilateCode and year
SHJP4 <- SHJP4 %>%
  group_by(AffiliateCode, year) %>%
  filter(n() == 1) %>%
  ungroup()
  
```

## Clean the data

必要ない可能性ある。

```{r clean-data}
# Remove "" from the column names of SHJP_JP
  names(SHJP4) <- gsub("", "", names(SHJP4))

```




# Ownership data with Japanese affiliates' basic data

Combine the Japanese ownership data "SHJP_JP" with the Japanese affiliates' basic data "FA"


```{r combine-FA-data}
# Merge Japanese parent firms' ownership data (SHJP) and Japanese affiliates' basic data (FA) 
  SHJP5 <- left_join(SHJP4, FA3, 
                         by = c("AffiliateCode" = "AffiliateCode", 
                                "year" = "year"))
# Remove duplicates in terms of AffilateCode and year
  SHJP5 <- SHJP5 %>%
    group_by(AffiliateCode, year) %>%
    filter(n() == 1) %>%
    ungroup()
```



```{r}
# Sort the data by KSKJPCode, iso, and year
  SHJP5 = SHJP5[order(SHJP5$JPCode, 
                      SHJP5$iso, 
                      SHJP5$year), ]
```


# Japanese affiliates' basic data with Ownership data

```{r combine-FA-data2}
# Combine the Japanese affiliates' basic data (FA) with the ownership data (SHJP_JP)
FA4 <- left_join(FA3, SHJP4, 
                          by = c("AffiliateCode" = "AffiliateCode", 
                                 "year" = "year"))

# Remove duplicates in terms of AffilateCode and year
FA4 <- FA4 %>%
  group_by(AffiliateCode, year) %>%
  filter(n() == 1) %>%
  ungroup()
```


```{r}
# order AffiliateCode year JPCode
  FA4 = FA4[order(FA4$AffiliateCode, 
                  FA4$year, 
                  FA4$JPCode), ]

# Move AffiliateCode year JPCode
  FA4 <- FA4 %>%
    select(AffiliateCode, year, JPCode, everything())

```




# Save the data


```{r save-data}
# Save the data as RDS file
  rio::export(SHJP5, "../Data_output/SHJP5.rds")
  rio::export(FA4, "../Data_output/FA4.rds")

```


