---
title: "Survival data"
author: "Ayumu Tanaka"
date: "2024-05-23"
output:
  html_document:
    toc: true
    toc_float: true
    number_sections: yes
    #keep_md: true
#bibliography: ref.bib
#link-citations: yes
---

```{r setup-chunk, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, # show R code
                      cache = FALSE, # do not cache results
                      message=FALSE, # do not show messages
                      warning=FALSE) # do not show warnings

```



# Preparation


```{r preparation}
# Remove all data
rm(list = ls())

# Load the necessary libraries
library("rio")           # For importing data 
library("tidyverse")     # For data manipulation
library("countrycode")   # For creating the country ISO codes
library("Hmisc")         # For labeling the variables
```


# Load the data

## Input data
- "../Data_output/FA5.rds"

## Output data
- "../Data_output/FA5.rds"
- "../Data_output/aff_last.rds"
- "../Data_output/parent.rds"
- "../Data_output/parent_last.rds"


```{r load-data}
## Remove the all data
rm(list = ls())

# Load "FA5.rds"
library(rio)
FA5 <- rio::import("../Data_output/FA5.rds")

```



# Rename the variables
```{r rename-variables}
# Rename the variables
FA5 <- FA5 %>%
  rename(firm = Parent_NameAlphabet,
         Ratio = JOwnRatio,
         Parent_SectorCode = Parent_SectorCode2009,
         Parent_SectorName = Parent_SectorNameAlph,
         Parent_SectorClassNameAlph = Parent_SectorClassNameAlph,
         Aff_size = PayrollNumber,
         EU = eu, 
         EU_all = euall,
         #Political_Stability = pvr, 
         #Government_Effectiveness = ger,
         #Regulatory_Quality = rqr,
         #Rule_of_Law = rlr, 
         #Control_of_Corruption = ccr,
         Dist = dist)
```


# Making the affiliate-level data
## Calculate the survival years by firm and country iso code

```{r calculate-survival-years-affiliate}
# Calculate the survival years by affiliate and country iso code
FA5 <- FA5 %>% 
  group_by(AffiliateCode, iso) %>% 
  mutate(survival_years = year - min(year) + 1)


FA5 <- FA5 %>% 
  group_by(AffiliateCode, iso) %>% 
  mutate(min_year = min(year) )

# Check the distribution of the survival years
hist(FA5$survival_years)

```


## Keep the observation of the last year by each firm

```{r keep-last-year-affiliate}

# Keep the observation of the last year by each affiliate
  aff_last <- FA5 %>% 
    group_by(AffiliateCode, iso) %>% 
    filter(year == max(year))
```


## Identify the affiliate that disappeared before the last year

```{r identify-disappeared-affiliate}
# Make the variable that Identify the firms that disappeared before the last year
aff_last <- aff_last %>% 
  mutate(censored = ifelse(year == max(aff_last$year), 1, 0))

# exit= 0 if censored==1, exit=1 if event==1
aff_last$exit <- ifelse(aff_last$censored == 1, 0, 1)

# Table by exit & censored
table(aff_last$exit, aff_last$censored)

# Move "censored" and "survival_years" to the column after JPCode, iso, and year
aff_last <- aff_last %>% 
  select(AffiliateCode, JPCode, iso, year, min_year, survival_years, censored, everything())

# Sort the data by "KSKJPCode", "iso", and "year"
aff_last <- aff_last %>% 
  arrange(iso, AffiliateCode, year)

```

## Create a dummy variable for GBR and Brexit
```{r create-dummy-variable-affiliate}
# Create a dummy variable for iso == GBR
  aff_last$GBR <- NULL 
  aff_last <- aff_last %>% 
    mutate(GBR = ifelse(iso == "GBR", 1, 0))
  
# Create a dummy variable for iso == GBR & year >= 2016
aff_last <- aff_last %>% 
  mutate(Brexit = ifelse(iso == "GBR" & year >= 2016, 1, 0))

# Display the number of observations by "GBR" and "Brexit"
table(aff_last$GBR, aff_last$Brexit)
```   


## Ownership ratio

- ParentJPOwnRatio: total ownership ratio of all Japanese parent firms
- Ratio: ownership ratio of the top Japanese parent firm

- Ratioは欠損値が少しある。

```{r ratio}
#FA6$Ratio <- FA6$Ratio 
FA5$Ratio <-    FA5$Ratio * (1/100)
FA5$RatioAll <- FA5$ParentJPOwnRatio/100
FA5$ParentJPOwnRatio<- NULL

# Count if ParentJPOwnRatio > Ratio
FA5$D <- ifelse(FA5$RatioAll > FA5$Ratio, 1, 0)
table(FA5$D)
FA5$D <- NULL

# Missing values in Ratio
table(is.na(FA5$Ratio))
table(is.na(FA5$RatioAll))

# If Ratio is missing, then replace it with ParentJPOwnRatio
FA5$Ratio <- ifelse(is.na(FA5$Ratio), FA5$RatioAll, FA5$Ratio)
```





# Making the parent-level data
## Collapse the data by firm, iso, and year

It takes significant time to collapse the data by firm, iso, and year with the `tidyverse` package. Therefore, I use `data.table` to collapse the data.



```{r collapse-data-by-firm-iso-year}
library(data.table)
# Convert FA5 to data.table
setDT(FA5)
# Group by JPCode, iso, and year and perform summarization
parent <- FA5[, .(
  N_Aff = .N,
  firm = first(firm),
  Ratio = mean(Ratio),
  Parent_SectorCode = first(Parent_SectorCode),
  Parent_SectorName = first(Parent_SectorName),
  Parent_SectorClass = first(Parent_SectorClass),
  Parent_SectorClassNameAlph = first(Parent_SectorClassNameAlph),
  Aff_size = sum(Aff_size),
  EU = first(EU),
  EU_all = first(EU_all),
  countryname = first(countryname),
  GDP_PPP = first(GDP_PPP),
  GDP_per_capita = first(GDP_per_capita),
  #Political_Stability = first(Political_Stability),
  #Government_Effectiveness = first(Government_Effectiveness),
  #Regulatory_Quality = first(Regulatory_Quality),
  #Rule_of_Law = first(Rule_of_Law),
  #Control_of_Corruption = first(Control_of_Corruption),
  Dist = first(Dist),
  N_Aff_EU = first(N_Aff_EU),
  N_Aff_GBR = first(N_Aff_GBR)
), by = .(JPCode, iso, year)]

```


The following code is too slow to run. I will use the code above instead.

```
library(dplyr)

# Calculate the number of observation by "JPCode", "iso", and "year"
parent <- FA5 %>% 
  group_by(JPCode, iso, year) %>% 
  summarise(N_Aff = n(), 
            firm = first(firm), 
            Ratio = mean(Ratio),
            Parent_SectorCode = first(Parent_SectorCode), 
            Parent_SectorName = first(Parent_SectorName),
            Parent_SectorClass = first(Parent_SectorClass),
            Parent_SectorClassNameAlph = first(Parent_SectorClassNameAlph),
            Aff_size = sum(Aff_size),
            EU = first(EU), 
            EU_all = first(EU_all), 
            countryname = first(countryname),
            GDP_PPP = first(GDP_PPP), 
            GDP_per_capita = first(GDP_per_capita),
            Political_Stability = first(Political_Stability), 
            Government_Effectiveness = first(Government_Effectiveness), 
            Regulatory_Quality = first(Regulatory_Quality),
            Rule_of_Law = first(Rule_of_Law), 
            Control_of_Corruption = first(Control_of_Corruption),
            Dist = first(Dist),
            N_Aff_EU = first(N_Aff_EU),
            N_Aff_GBR = first(N_Aff_GBR),
            )

```

## Calculate the survival years by firm and country iso code

```{r calculate-survival-years}
# Calculate the survival years by firm and country iso code
parent <- parent %>% 
  group_by(JPCode, iso) %>% 
  mutate(survival_years = year - min(year) + 1)

# Check the distribution of the survival years
hist(parent$survival_years)

```


## Keep the observation of the last year by each firm

```{r keep-last-year}

# Keep the observation of the last year by each firm
  parent_last <- parent %>% 
    group_by(JPCode, iso) %>% 
    filter(year == max(year))
```

## Identify the firms that disappeared before the last year

```{r identify-disappeared-firms}
# Make the variable that Identify the firms that disappeared before the last year
parent_last <- parent_last %>% 
  mutate(censored = ifelse(year == max(parent_last$year), 1, 0))

# exit= 0 if censored==1, exit=1 if event==1
parent_last$exit <- ifelse(parent_last$censored == 1, 0, 1)

# Table by exit & censored
table(parent_last$exit, parent_last$censored)

# Move "censored" and "survival_years" to the column after JPCode, iso, and year
parent_last <- parent_last %>% 
  select(JPCode, iso, year, censored, survival_years, everything())

# Sort the data by "KSKJPCode", "iso", and "year"
parent_last <- parent_last %>% 
  arrange(JPCode, iso, year)

```


## Create a dummy variable for GBR and Brexit
```{r create-dummy-variable}
# Create a dummy variable for iso == GBR
parent_last <- parent_last %>% 
  mutate(GBR = ifelse(iso == "GBR", 1, 0))

# Create a dummy variable for iso == GBR & year >= 2016
parent_last <- parent_last %>% 
  mutate(Brexit = ifelse(iso == "GBR" & year >= 2016, 1, 0))

# Display the number of observations by "GBR" and "Brexit"
table(parent_last$GBR, parent_last$Brexit)
```   


## Save the data
```{r save-data}
# Save the data
rio::export(parent, "../Data_output/parent.rds")
rio::export(parent_last, "../Data_output/parent_last.rds")


# Save the data
rio::export(FA5, "../Data_output/FA6.rds")
rio::export(aff_last, "../Data_output/aff_last.rds")

rio::export(FA5, "../Data_output/FA6.dta")


```





