---
title: "Sector Codes: 東洋経済データの産業分類の整理"
author: "Ayumu Tanaka"
date: "2024-05-18"
output:
  html_document:
    toc: true
    toc_float: true
    number_sections: yes
#bibliography: ref.bib
link-citations: yes
---

```{r setup-chunk, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, # Display codes
                      cache = FALSE, # do not Cache the results
                      message=FALSE, # Suppress messages
                      warning=FALSE) # Suppress warnings

```

# Preparation


```{r preparation}
# Remove all data
rm(list = ls())

# Load the necessary libraries
library("rio")           # For importing data 
library("tidyverse")     # For data manipulation
library("countrycode")   # For creating the country ISO codes
library("Hmisc")         # For labeling the variables
```




# Load the data データ読み込み

- "../Data_output/FA.rds"
- "../Data_output/JP.rds"

以下のデータを読み込む。

- "JP": 日本の親会社の財務データ
- "FA": 日本の海外子会社の基本データ

```{r load-data}

JP <- import("../Data_output/JP.rds")
FA <- import("../Data_output/FA.rds")
```


# Sector Codes 産業分類コード

```{r sector-codes}

# Import the sector codes correspondence table for 1990, 2000, and 2009 
SectorCode_Map <- import("../Data_raw/KSK_Code_tanaka2024.xlsx",
          sheet = "SectorCode_Map", skip = 3)
# Converting the SectorCode into numeric
SectorCode_Map$SectorCode1990 = as.numeric(SectorCode_Map$SectorCode1990)
SectorCode_Map$SectorCode2000 = as.numeric(SectorCode_Map$SectorCode2000)
SectorCode_Map$SectorCode2009 = as.numeric(SectorCode_Map$SectorCode2009)

# Import the sector codes for 2009
SectorCode2009 <- import("../Data_raw/KSK_Code_tanaka2024.xlsx",
            sheet = "SectorCode2009", skip = 3)
SectorCode2009 = SectorCode2009 %>%
  select(c(SectorCode2009, SectorName2009, SectorNameAlph,
           SectorClass, SectorClassName, SectorClassNameAlph))

# Converting the SectorCode into numeric
SectorCode_Map$SectorCode2009 = as.numeric(SectorCode_Map$SectorCode2009)

```


# Parent-level data 親会社レベル

Combining the sector codes with JP data

## Step 1 - 1990

```{r combine-sector-codes-JP}

## Merging JP with "SectorCode_Map" using SectorCode1990 as a key
  JP <- left_join(JP, SectorCode_Map %>% 
                    select(c(SectorCode1990, SectorCode2009)), 
                  by = c("Parent_SectorCode1990" = "SectorCode1990"))

```


```{r}
## Replacing "Parent_SectorCode2009" with "SectorCode2009" if "Parent_SectorCode1990" is non-missing
  JP <- JP %>%
    mutate(Parent_SectorCode2009 = 
             ifelse(!is.na(Parent_SectorCode1990), SectorCode2009, Parent_SectorCode2009))


## Temporarily remove "SectorCode2009" from JP data
  JP$SectorCode2009 = NULL

```


## Step 2 - 2000

```{r}

## Merging JP with "SectorCode_Map" using SectorCode2000 as a key
  JP <- left_join(JP, SectorCode_Map %>% 
                    select(c(SectorCode2000, SectorCode2009)), 
                  by = c("Parent_SectorCode2000" = "SectorCode2000"))

## Replacing "SectorCode2009" with "SectorCode2009" if "SectorCode2000" is non-missing
  JP <- JP %>%
    mutate(Parent_SectorCode2009 = 
             ifelse(!is.na(Parent_SectorCode2000), SectorCode2009, Parent_SectorCode2009))  
   
## Remove "SectorCode2009" from JP data
  JP$SectorCode2009 = NULL
  
```


## Step 3 Modification


```{r}

## replacing SectorCode2009 for 3000 and 8000
## Replacing SectorCode2009 = 3000 if SectorCode1990 == 3000
  JP$Parent_SectorCode2009[JP$Parent_SectorCode1990 == 3000&is.na(JP$Parent_SectorCode2009)] = 5210 # Other wholesaling
## Replacing SectorCode2009 = 3000 if SectorCode1990 == 3000
  JP$Parent_SectorCode2009[JP$Parent_SectorCode1990 == 8000&is.na(JP$Parent_SectorCode2009)] = 7910 #Other Services


## Remove "SectorCode1990" & "SectorCode2000"
  JP$Parent_SectorCode1990 = NULL
  JP$Parent_SectorCode2000 = NULL
```

## Step 4 Modification

```{r}


## Create the lagged and lead sector codes
  JP <- JP %>%
    group_by(JPCode) %>%
    mutate(Parent_SectorCode2009L1 = lag(Parent_SectorCode2009, n=1))
  
  JP <- JP %>%
    group_by(JPCode) %>%
    mutate(Parent_SectorCode2009F1 = lead(Parent_SectorCode2009, n=1))

## Replacing the missing SectorCode2009 with SectorCode2009L1 if SectorCode2009 is missing
  JP$Parent_SectorCode2009[is.na(JP$Parent_SectorCode2009)] <- JP$Parent_SectorCode2009L1[is.na(JP$Parent_SectorCode2009)]

## Replacing the missing SectorCode2009 with SectorCode2009F1 if SectorCode2009 is missing
  JP$Parent_SectorCode2009[is.na(JP$Parent_SectorCode2009)] <- JP$Parent_SectorCode2009F1[is.na(JP$Parent_SectorCode2009)]
  

## Remove the lagged and lead sector codes
  JP$Parent_SectorCode2009L1 <- NULL
  JP$Parent_SectorCode2009F1 <- NULL

```

## Step 5 - Combine with SectorCode2009

```{r}

## Combine the "JP" data with the "SectorCode2009" data
  SectorCode2009$SectorCode2009 <- as.numeric(SectorCode2009$SectorCode2009)
  JP <- left_join(JP, SectorCode2009, 
                  by = c("Parent_SectorCode2009" = "SectorCode2009"))
  
```


## Step 6

```{r}
## Rename 
  names(JP)[names(JP) == "SectorClass"] <-         "Parent_SectorClass"
  names(JP)[names(JP) == "SectorClassName"] <-     "Parent_SectorClassName"
  names(JP)[names(JP) == "SectorClassNameAlph"] <- "Parent_SectorClassNameAlph"
  names(JP)[names(JP) == "SectorName2009"] <-      "Parent_SectorName2009"
  names(JP)[names(JP) == "SectorNameAlph"] <-      "Parent_SectorNameAlph"
  
```


# Affiliate-level data 子会社レベル

Combining the sector codes with FA data


## Step 1

```{r combine-sector-codes-FA}

## Merging FA with SectorCOde_Map using SectorCode1990 as a key
  FA <- left_join(FA, SectorCode_Map %>% 
                    select(c(SectorCode1990, SectorCode2009)), 
                  by = c("FA_SectorCode1990" = "SectorCode1990"))

  FA <- FA %>%
    mutate(FA_SectorCode2009 = 
             ifelse(!is.na(FA_SectorCode1990), SectorCode2009, FA_SectorCode2009))

## Remove "SectorCode2009" from FA data
  FA$SectorCode2009 = NULL
```



## Step 2
```{r}
## Merging FA with SectorCode_Map using SectorCode2000 as a key
  FA <- left_join(FA, SectorCode_Map %>% 
                    select(c(SectorCode2000, SectorCode2009)), 
                  by = c("FA_SectorCode2000" = "SectorCode2000"))

  FA <- FA %>%
    mutate(FA_SectorCode2009 = 
             ifelse(!is.na(FA_SectorCode2000), SectorCode2009, FA_SectorCode2009))
  
## Remove "SectorCode2009" from FA data
  FA$SectorCode2009 = NULL
```
  
  
## Step 3
```{r}
## Remove "KSFSectorCode1900" & "KSFSectorCode2000"
  FA$FA_SectorCode1990 = NULL
  FA$FA_SectorCode2000 = NULL
```

  
## Step 4
```{r}
## SectorClass: SectorClass
  ## SectorClass: SectorClass
  FA <- left_join(FA, SectorCode2009, 
                  by = c("FA_SectorCode2009" = "SectorCode2009"))
```


## Step 5

```{r}
## Rename 
  names(FA)[names(FA) == "SectorClass"] <-         "FA_SectorClass"
  names(FA)[names(FA) == "SectorClassName"] <-     "FA_SectorClassName"
  names(FA)[names(FA) == "SectorClassNameAlph"] <- "FA_SectorClassNameAlph"
  names(FA)[names(FA) == "SectorName2009"] <-      "FA_SectorName2009"
  names(FA)[names(FA) == "SectorNameAlph"] <-      "FA_SectorNameAlph"
  
```


# Remove duplicates

```{r remove-duplicates}
# Remove duplicates in terms of JPCode and year
JP <- JP %>%
  group_by(JPCode, year) %>%
  filter(row_number() == 1) %>%
  ungroup()

# Remove duplicates in terms of AffiliateCode and year
FA <- FA %>%
  group_by(AffiliateCode, year) %>%
  filter(row_number() == 1) %>%
  ungroup()

```


# Export the data データ保存

````{r export-data}
  rio::export(JP, "../Data_output/JP2.rds")
  rio::export(FA, "../Data_output/FA2.rds")
```

