---
title: "Affiliate data & Country-level data: 子会社データと国データの接続"
author: "Ayumu Tanaka"
date: "2024-05-18"
output:
  html_document:
    toc: true
    toc_float: true
    number_sections: yes
#bibliography: ref.bib
link-citations: yes
---

```{r setup-chunk, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, # Display codes
                      cache = FALSE, # do not Cache the results
                      message=FALSE, # Suppress messages
                      warning=FALSE) # Suppress warnings

```

# Preparation


```{r preparation}
# Remove all data
rm(list = ls())

# Load the necessary libraries
library("rio")           # For importing data 
library("tidyverse")     # For data manipulation
library("countrycode")   # For creating the country ISO codes
library("Hmisc")         # For labeling the variables
```




# Load the data データ読み込み


以下のデータを読み込む。

- "FA2": 日本の海外子会社の基本データ

```{r load-data}

FA2 <- import("../Data_output/FA2.rds")
```




# ISO country codes

Creating the country ISO codes using `countrycode` package for the affiliate data "FA2"


```{r countrycode}

# Replace countrynames
# Example) Replace "Estoniya" with "Republic of Estonia" with gsub()
FA2$NationNameAlph = gsub("Estoniya", "Republic of Estonia", FA2$NationNameAlph)
FA2$NationNameAlph = gsub("Latviya", "Republic of Latvia", FA2$NationNameAlph)
FA2$NationNameAlph = gsub("Lebanese Republic", "Republic of Lebanon", FA2$NationNameAlph)
FA2$NationNameAlph = gsub("Portuguese Republic", "Portugal", FA2$NationNameAlph)
FA2$NationNameAlph = gsub("Republic of Cote D'ivire", "Ivory Coast", FA2$NationNameAlph)
FA2$NationNameAlph = gsub("Slovenija", "Slovenia", FA2$NationNameAlph)
FA2$NationNameAlph = gsub("New Yugoslavia", "Yugoslavia", FA2$NationNameAlph) # Former Yugoslavia
FA2$NationNameAlph = gsub("Serbia and Montenegro", "Yugoslavia", FA2$NationNameAlph) # Former Yugoslavia
FA2$NationNameAlph = gsub("Socialist Federal Republic of Yugoslavia", "Yugoslavia", FA2$NationNameAlph) # Former Yugoslavia
FA2$NationNameAlph = gsub("Socialist Federal Republic of Yugoslavia", "Yugoslavia", FA2$NationNameAlph) # Former Yugoslavia
FA2$NationNameAlph = gsub("Netherlands Antilles", "Netherlands", FA2$NationNameAlph)
FA2$NationNameAlph = gsub("Saipan", "United States", FA2$NationNameAlph)
FA2$NationNameAlph = gsub("The Cooperative Republic of Guyana", "Guyana", FA2$NationNameAlph)
FA2$NationNameAlph = gsub("Republic of Namibia", "Namibia", FA2$NationNameAlph)


# Create the country ISO codes for Japan
  FA2 <- FA2 %>% 
    mutate(iso = countrycode(NationNameAlph, origin = "country.name", destination = "iso3c"))

# Move the column "iso" after the column NationNameAlph
  FA2 <- FA2 %>% 
    select(NationNameAlph, iso, everything())
  
# Create countryname with countrycode package
  FA2 <- FA2 %>% 
    mutate(countryname = countrycode(iso, origin = "iso3c", destination = "country.name"))

# Remove "NationNameAlph"
  FA2$NationNameAlph = NULL
  
```

# EU dummy

Merging the EU dummy data with the affiliate data "FA2"

```{r EU-dummy}
# Load the EU dummy data
  EU <- import("../Data_raw/eu.dta")

# Make the euall column in the EU dummy data as 0
  EU$euall <- 1
  
# Label the column "euall" as "Former/current EU members"
  label(EU$euall) <- "Former/current EU members"

# Merge the EU dummy data with the affiliate data
  FA2 <- left_join(FA2, EU %>% select(iso_code, year, eu, euall), 
                                by = c("iso" = "iso_code", "year" = "year"))
  
# Replace the column "eu" if it is NA with 0
  FA2$eu[is.na(FA2$eu)] <- 0

# Replace the column "euall" if it is NA with 0
  FA2$euall[is.na(FA2$euall)] <- 0
  
# Move the columns "eu" and "europe" after the column "iso"
  FA2 <- FA2 %>% 
    select(iso, year, eu, euall, everything())

```

# WDI
Combine the FA2 data with the WDI data

```{r combine-WDI}
# Load the WDI.rds
library(rio)
  WDI <- import("../Data_raw/WDI.rds")
# Select the necessary columns
  WDI <- WDI %>% 
    select(iso3c, year, GDP_PPP, GDP_per_capita)
# Merge the WDI data with the affiliate data
  FA2 <- left_join(FA2, WDI, 
                   by = c("iso" = "iso3c", "year" = "year"))

```


# WGI

Combine the FA2 data with the WGI data

```
# Load the WGI.csv
  WGI <- import("../Data_output/WGI.rds")
# Merge the WDI data with the affiliate data
  FA2 <- left_join(FA2, WGI, 
                   by = c("iso" = "code", "year" = "year"))
```


# Distance

Combine the FA2 data with the distance data from the CEPII's Gravity database

```{r combine-CEPII}
# Load the CEPII's distance data
  distance <- import("../Data_raw/distance.dta")
# Keep the iso_o=="JPN" and iso_d=="iso"
  distance <- distance %>% 
    filter(iso3_o=="JPN")
# Select the necessary columns
  distance <- distance %>% 
    select(iso3_d, dist)
# Merge the distance data with the affiliate data
  FA2 <- left_join(FA2, distance,
                   by = c("iso" = "iso3_d"))
```


# Remove duplicates

```{r}
# Remove duplicates in terms of AffilateCode and year
FA2 <- FA2 %>%
  group_by(AffiliateCode, year) %>%
  slice(1) %>%
  ungroup()
```



# Export the data

```{r export-data}
rio::export(FA2, "../Data_output/FA3.rds")
```



