---
title: "Map of Brexit"
author: "Ayumu Tanaka"
date: "2024-06-22"
output:
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    #keep_md: true
---

```{r setup-chunk, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, # show R code
                      cache = FALSE, # do not cache results
                      message=FALSE, # show messages
                      warning=FALSE) # show warnings

```


# World map

- `ne_countries()': Get natural earth world country polygons
- `geom_sf()': Plot the world map


```{r}
library("ggplot2")
library("sf")
library("rnaturalearth")
library("rnaturalearthdata")

# Get natural earth world country polygons with `ne_countries()' function
world <- ne_countries(scale = "medium", returnclass = "sf")

# Replacing su_a3
world$su_a3[world$name=="Portugal"] <- "PRT"

# Subset the data
world2 <- world[,c("su_a3", "name", "name_ja", "continent", "label_x", "label_y", "geometry")]
# Set the theme to `theme_bw()'
theme_set(theme_bw())
# Plot the world map with `geom_sf()' function and `ggplot()'
ggplot(data = world2) + geom_sf()

```

# Affiliate-level
## Data on Number of Japanese affiliatess in countries

```{r}
# Load the data
library(rio)
N_Aff <- rio::import("../Data_output/N_Aff.rds")

# Include Swiss as Europe
N_Aff$EU[N_Aff$country=="CHE"] <- 1

# Subset of EU==1
N_Aff_Europe <- subset(N_Aff, EU==1)

# Data of 2010
N_Aff_Europe_2010 <- subset(N_Aff_Europe, year==2010)

# Combine the data with the world map
world_merged2010 <- merge(world2, N_Aff_Europe_2010, by.x = "su_a3", by.y = "country")

# Data of 2014
N_Aff_Europe_2014 <- subset(N_Aff_Europe, year==2014)

# Combine the data with the world map
world_merged2014 <- merge(world2, N_Aff_Europe_2014, by.x = "su_a3", by.y = "country")


# Data of 2020
N_Aff_Europe_2020 <- subset(N_Aff_Europe, year==2020)

# Combine the data with the world map
world_merged2020 <- merge(world2, N_Aff_Europe_2020, by.x = "su_a3", by.y = "country")

```

## Map of the Number of Japanese affiliates in Europe


- for the label, `geom_sf_text()` and `geom_sf_label()` are available. 
- The `geom_sf_label()` present the labels with white backgroud.
- The `geom_sf_text()` present the labels without background.
- The official document is [here](https://yutannihilation.github.io/ggsflabel/reference/geom_sf_label.html#details).
- The useful guide is [here](https://thegraphcourses.org/wp-content/uploads/2022/01/02_choropleth_maps_working_with_coordinates_labels_segments_and_points.html) and [here](https://yutani.rbind.io/post/geom-sf-text-and-geom-sf-label-are-coming/).

### 2010 with `geom_sf_text()`

- `theme(axis.text = element_blank(), axis.title = element_blank())` suppress the longitude and latitude.

```{r fig-map-aff-2010, dpi = 300}

# Plot the map of the number of Japanese affiliates in Europe

ggp2010 <-ggplot(data = world_merged2010) +
    geom_sf(aes(fill = N), alpha = 0.4) +
    scale_fill_distiller(name="N", palette = "Greens", direction=1, guide = NULL)+
  labs(title="N. of  affiliates in 2010",caption="") +
  coord_sf(xlim = c(-11, 32), ylim = c(70, 35), expand = TRUE)+
   theme(axis.text = element_blank(), axis.title = element_blank()) +
      geom_sf_text(
               aes(label = N), size = 2, color = "black", fontface = "bold",
               position = "dodge")  # label

ggp2010

```






### 2014

- `guide = NULL`: suppress the legend.

```{r fig-map-aff-2014, dpi = 300}

ggp2014 <-ggplot(data = world_merged2014) +
    geom_sf(aes(fill = N), alpha = 0.4) +
    scale_fill_distiller(name="N", palette = "Greens", direction=1, guide = NULL)+
  labs(title="N. of  affiliates in 2014",caption="") +
  coord_sf(xlim = c(-11, 32), ylim = c(70, 35), expand = TRUE)+
   theme(axis.text = element_blank(), axis.title = element_blank()) +
      geom_sf_text(
               aes(label = N), size = 2, color = "black", fontface = "bold",
               position = "dodge")  # label

ggp2014

```

### 2020

```{r fig-map-aff-2020, dpi = 300}

ggp2020 <-ggplot(data = world_merged2020) +
    geom_sf(aes(fill = N), alpha = 0.4) +
    scale_fill_distiller(name="N", palette = "Greens", direction=1, guide = NULL)+
  labs(title="N. of  affiliates in 2020",caption="") +
  coord_sf(xlim = c(-11, 32), ylim = c(70, 35), expand = TRUE)+
   theme(axis.text = element_blank(), axis.title = element_blank()) +
      geom_sf_text(
               aes(label = N), size = 2, color = "black", fontface = "bold",
               position = "dodge")  # label

ggp2020


```

## Compare the maps of 2010 and 2020

```{r fig-map-aff-2010-2020, dpi = 300}
#install.packages("gridExtra")               # Install gridExtra package
library("gridExtra")                        # Load gridExtra package
combined <- grid.arrange(ggp2010, ggp2020, nrow = 1)          # Apply grid.arrange function

library(ggplot2)
ggsave("../EPS/FigA1-map-aff-2010-2020.pdf", plot = combined, width = 10, height = 6, dpi = 300)
```

## Compare the maps of 2014 and 2020

```{r FigA1-map-aff-2014-2020, dpi = 300}
#install.packages("gridExtra")               # Install gridExtra package
library("gridExtra")                        # Load gridExtra package
combined <- grid.arrange(ggp2014, ggp2020, nrow = 1)          # Apply grid.arrange function

library(ggplot2)
ggsave("../EPS/FigA1-map-aff-2014-2020.pdf", plot = combined, width = 10, height = 6, dpi = 300)
```



# Parent-level
## Data on Number of Japanese parent firms in countries

```{r}
# Load the data "parent.rds"
library(rio)
parent <- rio::import("../Data_output/parent.rds")

```


## Collapse the parent data by iso and year

```{r}
# Collapse the data "parent" by iso and year
library(tidyverse)
N_Parent <- parent %>% 
  group_by(year, iso) %>% 
  summarise(N = n(),
            EU = first(EU_all),
            WN = sum(Ratio),
            Sector = first(Parent_SectorClassNameAlph),
            SectorClass = first(Parent_SectorClass))

# Include Swiss as Europe
N_Parent$EU[N_Parent$iso=="CHE"] <- 1

# Subset of EU==1
N_Parent_Europe <- subset(N_Parent, EU==1)

```

## Combine the parent data with the world map

```{r}
# Data of 2014
N_Parentt_Europe_2014 <- subset(N_Parent_Europe, year==2014)


# Combine the data with the world map
world_merged_parent2014 <- merge(world2, N_Parentt_Europe_2014, 
                                 by.x = "su_a3", by.y = "iso")

# Data of 2020
N_Parentt_Europe_2020 <- subset(N_Parent_Europe, year==2020)

# Combine the data with the world map
world_merged_parent2020 <- merge(world2, N_Parentt_Europe_2020, 
                                 by.x = "su_a3", by.y = "iso")

```


## Map of the Number of Japanese parent firms in Europe

### 2014

```{r fig-map-parent-2014, dpi = 300}
pmap2014 <- ggplot(data = world_merged_parent2014) +
    geom_sf(aes(fill = N), alpha = 0.4) +
    scale_fill_distiller(name="N", palette = "Greens", direction=1, guide = NULL)+
  labs(title="N. of firms in 2014",caption="") +
  coord_sf(xlim = c(-11, 32), ylim = c(70, 35), expand = TRUE)+
   theme(axis.text = element_blank(), axis.title = element_blank()) +
      geom_sf_text(
               aes(label = N), size = 2, color = "black", fontface = "bold",
               position = "dodge")  # label

pmap2014
```
### 2020

```{r fig-map-parent-2020, dpi = 300}
pmap2020 <- ggplot(data = world_merged_parent2020) +
    geom_sf(aes(fill = N), alpha = 0.4) +
    scale_fill_distiller(name="N", palette = "Greens", direction=1, guide = NULL)+
  labs(title="N. of firms in 2020",caption="") +
  coord_sf(xlim = c(-11, 32), ylim = c(70, 35), expand = TRUE)+
   theme(axis.text = element_blank(), axis.title = element_blank()) +
      geom_sf_text(
               aes(label = N), size = 2, color = "black", fontface = "bold",
               position = "dodge")  # label

pmap2020
```
## Compare the maps of 2014 and 2020

```{r fig-map-parent-2014-2020, dpi = 300}
#install.packages("gridExtra")               # Install gridExtra package
library("gridExtra")                        # Load gridExtra package
grid.arrange(pmap2014, pmap2020, nrow = 1)          # Apply grid.arrange function
```

# Combine 4 maps

```{r fig-map-all, dpi = 300}
#install.packages("gridExtra")               # Install gridExtra package
library("gridExtra")                        # Load gridExtra package
grid.arrange(ggp2014, ggp2020, pmap2014, pmap2020, nrow = 2)          # Apply grid.arrange function
```


