---
title: "Brexit: SDiD, Affiliate-level"
author: "Ayumu Tanaka"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    #keep_md: true
---

```{r setup-chunk, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, # show R code
                      cache = FALSE, # do not cache results
                      message=FALSE, # show messages
                      warning=FALSE) # show warnings

```


```{r packages}
# devtools::install_github("synth-inference/synthdid")
library(synthdid)
library(ggplot2)

set.seed(12345)
```

# Load the data

```{r data}
library(rio)
aff_highEU <- rio::import("../Data_output/ESTaff_highEU.dta")

# Keep years: 2010-2020
aff_highEU <- aff_highEU[aff_highEU$year >= 2010 & aff_highEU$year <= 2020, ]

```



```{r prepare}

aff_highEUb <- aff_highEU[, c("AffiliateCode", "country", "year", 
                              "exitit", "Brexit")]
# Rename "Brexit" to "treated" using names function
names(aff_highEUb)[names(aff_highEUb)=="Brexit"] = "treated"

table(aff_highEUb$year, aff_highEUb$treated)

# Convert to data frame
aff_highEUb <- as.data.frame(aff_highEUb)

# Arrange the data: country,  year, outcome, treated
aff_highEUb <- aff_highEUb[, c("AffiliateCode", "year", "exitit", "treated")]

```

# Set up the data for the synthetic DiD

- `sprintf` is a wrapper for the C function sprintf, that returns a character vector containing a formatted combination of text and variable values.

```{r sdid, message=FALSE,  warning=FALSE}

# panel.matrices to reshape the long data to wide data
setup = synthdid::panel.matrices(aff_highEUb, unit =1, time = 2, outcome = 3, treatment =4)
# synthdid_estimate to estimate the SDiD estimates
## Y: matrix of observed values
## N0: number of control group
## T0: number of pretreatment periods
aff_highEUb.tau.hat = synthdid::synthdid_estimate(setup$Y, setup$N0, setup$T0)
aff_highEUb.tau.hat
print(summary(aff_highEUb.tau.hat))

# vcov: Compute the variance-covariance matrix of Fitted Model Object
se = sqrt(vcov(aff_highEUb.tau.hat, method='placebo'))
se
# sprintf
label1 <- sprintf('Point estimate = %1.3f', aff_highEUb.tau.hat)
label2 <- sprintf('S.E.= %1.3f', se)
label3 <- summary( aff_highEUb.tau.hat)$dimensions
label4 <- sprintf('N = %1.0f', label3["N0"]+ label3["N1"])

label1
label2
label3
label4

sprintf('95%% CI (%1.2f, %1.2f)', aff_highEUb.tau.hat 
        - 1.96 * se, aff_highEUb.tau.hat + 1.96 * se)
```


# Plot the treatement effects
- parallel trends and control units

```{r Fig7-SDiD, dpi = 300}
plot(aff_highEUb.tau.hat, se.method='placebo')

# brexit.sdid1 < plot(brexit.tau.hat, se.method='placebo', scale_x_continuous(breaks=seq(2010,2020,2)))
g1 <- plot(aff_highEUb.tau.hat, se.method='placebo')
# Delete the unnesassary x-axis labels
g2 <- g1 + scale_x_continuous(breaks = ~ axisTicks(., log = FALSE)) + 
  # add labels
  annotate("text", x = 2016, y = 0.1, label = label1, size = 3) +
  annotate("text", x = 2016, y = 0.05, label = label2, size = 3) +
  annotate("text", x = 2016, y = 0, label = label4, size = 3) 

g2

# Save the plot
ggsave("../EPS/Fig7-SDiD.eps", dpi = 300,
       width=8, height=6)
ggsave("../EPS/Fig7-SDiD.png", dpi = 300,
       width=8, height=6)
ggsave("../EPS/Fig7-SDiD.pdf", dpi = 300,
       width=8, height=6)

```

## Weight

- Weight of control units, $\omega_i$


```{r weight, fig.width=7, fig.height=4}
synthdid_units_plot(aff_highEUb.tau.hat, se.method='placebo')
#ggsave("brexit.control.png")
```


## Check the parallel trends


```{r fig_parallel_trends, dpi = 300}
g3 <- plot(aff_highEUb.tau.hat, overlay=1,  se.method='placebo')
# Delete the unnecessary x-axis labels
g4 <- g3 + scale_x_continuous(breaks = ~ axisTicks(., log = FALSE)) 
g4
#ggsave("brexit.parallel_trends.png")
```


# DiD and SDiD

```{r}
# SC
#aff_highEUb.tau.sc   = sc_estimate(setup$Y, setup$N0, setup$T0)
# DiD
aff_highEUb.tau.did  = did_estimate(setup$Y, setup$N0, setup$T0)
# DiD, SC, SDiD。
aff_highEUb.estimates = list(aff_highEUb.tau.did, aff_highEUb.tau.hat)
# Name the results
names(aff_highEUb.estimates) = c('DiD', 'SDiD')
```


```{r}
# Print the results
print(unlist(aff_highEUb.estimates))
```


## Plot the DiD and SDiD results
```{r fig_sdid_did_sc, dpi = 300}
g5 <- synthdid_plot(aff_highEUb.estimates, se.method='placebo')
g6 <- g5 + scale_x_continuous(breaks = ~ axisTicks(., log = FALSE)) 
g6
#ggsave("brexit.sdid_did_sc.png")
```




