---
title: "Brexit: SDiD, SC, DiD. New Entry"
author: "Ayumu Tanaka"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    number_sections: true
   # keep_md: true
---

```{r setup-chunk, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, # show R code
                      cache = FALSE, # do not cache results
                      message=FALSE, # show messages
                      warning=FALSE) # show warnings

```


```{r packages}
# devtools::install_github("synth-inference/synthdid")
library(synthdid)
library(ggplot2)
library(dplyr)

set.seed(12345)
```

# Load the data


```{r data}
library(rio)
Data <- rio::import("../Data_output/collapse_industry.dta")

Data$FA_Sector <- Data$FA_SectorCode2009
Data$FA_SectorCode2009 <- NULL

# Keep years: 2010-2020
DataA <- Data[Data$year >= 2010 & Data$year <= 2020, ]


# Keep the EU countries
DataA <- DataA[DataA$EU == 1, ]

# Keep high-income EU countries
EU_HI <- c("AUT", "BEL", "DNK", "FIN", "FRA", "DEU", "IRL", "ITA", "LUX", "NLD", "SWE", "GBR")
DataA <- DataA[DataA$iso %in% EU_HI, ]

# Make a pair ID for the pair of iso and FA_sector
#DataA <- DataA %>%
#  mutate(pair = group_indices(., iso, FA_Sector))

```


# Make the balanced panel

```{r make-balanced-panel}

library(plm)
library(dplyr)
library(tidyr)

DataB <- DataA %>%
  # All combinations of iso - FA_Sector - year
  complete(iso, FA_Sector, year)

# Pair ID of iso & FA_Sector
DataB <- DataB %>%
  mutate(pair = group_indices(., iso, FA_Sector))

# Drop if iso==""
DataB <- DataB %>%
  filter(iso != "")
# Drop if FA_Sector==0
DataB <- DataB %>%
  filter(FA_Sector != 0)

# Make the balanced panel
#DataB <- plm::make.pbalanced(DataA, balance.type = c("fill"), index = c("iso", "year"))

# Replace NA with 0 for "N" column
DataB$N[is.na(DataB$N)] <- 0

```



```{r prepare}

# treated = 1 if iso == "GBR" and year >= 2016
# treated = 0 if iso != "GBR" and year < 2016
DataB$treated <- ifelse(DataB$iso == "GBR" & DataB$year >= 2016, 1, 0)

DataB <- DataB[, c("iso", "year", 
                              "N", "pair", "treated")]

table(DataB$year, DataB$treated)

# Convert to data frame
DataB <- as.data.frame(DataB)

# Arrange the data: country,  year, outcome, treated
DataB <- DataB[, c("pair", "year", "N", "treated")]

```



# Synthetic DiD


```{r sdid, message=FALSE,  warning=FALSE}

# Set up the data for the Synthetic DiD analysis
# panel.matrices to reshape the long data to wide data
setup = synthdid::panel.matrices(DataB, 
                                 unit =1, 
                                 time = 2, 
                                 outcome = 3, 
                                 treatment =4)
# synthdid_estimate to estimate the SDiD estimates
## Y: matrix of observed values
## N0: number of control group
## T0: number of pretreatment periods
estimateSDiD = synthdid::synthdid_estimate(setup$Y, setup$N0, setup$T0)
estimateSDiD
print(summary(estimateSDiD))

# vcov: Compute the variance-covariance matrix of Fitted Model Object
seSDiD = sqrt(vcov(estimateSDiD, method='placebo'))
seSDiD


```


- `sprintf` is a wrapper for the C function sprintf, that returns a character vector containing a formatted combination of text and variable values.

```{r label}
# sprintf
label1 <- sprintf('Point estimate = %1.3f', estimateSDiD)
label2 <- sprintf('S.E.= %1.3f', seSDiD)
label3 <- sprintf('95%% CI (%1.3f, %1.3f)', 
                  estimateSDiD - 1.96 * seSDiD, 
                  estimateSDiD + 1.96 * seSDiD)
label4 <- summary( estimateSDiD)$dimensions
label5 <- sprintf('N = %1.0f', label4["N0"]+ label4["N1"])

label1
label2
label3
```


# Plot the treatement effects
- parallel trends and control units

```{r Fig6_SDiD, dpi = 300}
plot(estimateSDiD, se.method='placebo')

# brexit.sdid1 < plot(brexit.tau.hat, se.method='placebo', scale_x_continuous(breaks=seq(2010,2020,2)))
g1 <- plot(estimateSDiD, se.method='placebo')
# Delete the unnesassary x-axis labels
g2 <- g1 + scale_x_continuous(breaks = ~ axisTicks(., log = FALSE)) + 
  # add label1 & label2
  annotate("text", x = 2016, y = 0.15, label = label1, size = 3) +
  annotate("text", x = 2016, y = 0.10, label = label2, size = 3) +
  annotate("text", x = 2016, y = 0.05, label = label3, size = 3) +
  annotate("text", x = 2016, y = 0.00, label = label5, size = 3) 

g2
    
# Save the plot
ggsave("../EPS/Fig9-SDiD-Entry.eps", dpi = 300,
       width=8, height=6)
ggsave("../EPS/Fig9-SDiD-Entry.png", dpi = 300,
       width=8, height=6)
ggsave("../EPS/Fig9-SDiD-Entry.pdf", dpi = 300,
       width=8, height=6)

```

## Weight

- Weight of control units, $\omega_i$


```{r weight, fig.width=7, fig.height=4}
synthdid_units_plot(estimateSDiD, se.method='placebo')
#ggsave("brexit.control.png")
```


## Check the parallel trends


```{r fig_parallel_trends, dpi = 300}
g3 <- plot(estimateSDiD, overlay=1,  se.method='placebo')
# Delete the unnecessary x-axis labels
g4 <- g3 + scale_x_continuous(breaks = ~ axisTicks(., log = FALSE)) 
g4
#ggsave("brexit.parallel_trends.png")
```


# DiD and SDiD

```{r}
# Estimates
estimateSC   = sc_estimate(setup$Y, setup$N0, setup$T0)
estimateDiD  = did_estimate(setup$Y, setup$N0, setup$T0)

# SE
seSC = sqrt(vcov(estimateSC, method='placebo'))
seDiD = sqrt(vcov(estimateDiD, method='placebo'))

# CI
CISC = sprintf('95%% CI (%1.3f, %1.3f)', 
               estimateSC - 1.96 * seSC, 
               estimateSC + 1.96 * seSC)
CIDiD = sprintf('95%% CI (%1.3f, %1.3f)', 
                estimateDiD - 1.96 * seDiD, 
                estimateDiD + 1.96 * seDiD)
CISDiD = sprintf('95%% CI (%1.3f, %1.3f)', 
                  estimateSDiD - 1.96 * seSDiD, 
                  estimateSDiD + 1.96 * seSDiD)

# List of Estimates, SE, and CI. 3*3
DataB.estimates = list(estimateDiD, estimateSC, estimateSDiD)
DataB.se = list(seDiD, seSC, seSDiD)
DataB.CI = list(CIDiD, CISC, CISDiD)

# Name the results
names(DataB.estimates) = c('DiD', 'SC', 'SDiD')
names(DataB.se) = c('DiD', 'SC', 'SDiD')
names(DataB.CI) = c('DiD', 'SC', 'SDiD')

```


```{r}
# Print the results
print(unlist(DataB.estimates))
print(unlist(DataB.se))
print(unlist(DataB.CI))

```


## Plot the DiD and SDiD results

```{r fig_sdid_did_sc, dpi = 300}
g5 <- synthdid_plot(DataB.estimates, se.method='placebo')
g6 <- g5 + scale_x_continuous(breaks = ~ axisTicks(., log = FALSE)) 
g6
#ggsave("brexit.sdid_did_sc.png")
```





